---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rstudioprefswitcher

<!-- badges: start -->

<!-- badges: end -->

The goal of rstudioprefswitcher is to provide a programmatic tool for switching RStudio preferences. It's designed mostly for instructors who want to switch between personal preferences and default RStudio preferences.

This package is a work in progress but is not intended for release to CRAN.

## Installation

This package is not intended for CRAN, please install with remotes

``` r
remotes::install_github("charliejhadley/rstudioprefswitcher")
```

## How to use

Let's assume your custom settings are currently set, but to make sure there's a drammatic change let's programmatically change the theme to something that looks like the Matrix as follows:

```{r}
rstudioapi::writeRStudioPreference("editor_theme", "Gob")
```

Now let's save this combination of settings as "matrix_theme"

```{r}
library("rstudioprefswitcher")
prefs_save(preferences_name = "matrix_theme")
```

So we can then reapply these settings, let's change to a "light" theme.

```{r}
rstudioapi::writeRStudioPreference("editor_theme", "Tomorrow")
```

Now let's set our preferences back to "matrix_theme", note that `prefs_set()` will reload RStudio to ensure all settings are applied.

```{r}
prefs_set(preferences_name = "matrix_theme")
```

### Resetting defaults

At present [it appears the only way to reset](https://github.com/rstudio/rstudio/issues/9217) your preferences programmatically is to delete the preference file. This can be achieved with `prefs_reset_to_defaults()`

```{r}
prefs_reset_to_defaults()
```

**However**. RStudio maintains several default preferences from the R Console (R GUI) that contribute to poor code reproducibility, specifically:

- Asking to save .RData on exit
- Restoring .RData at startup 
- Always save History

You are strongly encouraged to run `prefs_improve_reproducibility()` after `prefs_reset_to_defaults()` to improve the reproducibility of your code.

```{r}
prefs_improve_reproducibility()
```
