---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rstudioprefswitcher

<!-- badges: start -->

<!-- badges: end -->

The goal of rstudioprefswitcher is to provide a programmatic tool for switching RStudio preferences. It's designed mostly for instructors who want to switch between personal preferences and default RStudio preferences.

At this point the package is likely to be a stub and not further developed by the current maintainer. It's also **untested on Windows so returns an error :woman_shrugging:**.

## Installation

This package is not intended for CRAN, please install with remotes

``` r
remotes::install_github("charliejhadley/rstudioprefswitcher")
```

## Details

[Maëlle Salmon](https://twitter.com/ma_salmon) has written an awesome article on various methods for [how packages can store user preferences](https://blog.r-hub.io/2020/03/12/user-preferences/#using-a-config-file). This package makes use of the [`{rappsdirs}`](https://rappdirs.r-lib.org/) package for storing preferences.

## Example

You've already customised your RStudio installation lots, but let's just make one more easy to see change:

-   hide the taskbar

```{r}
rstudioapi::writeRStudioPreference("toolbar_visible", FALSE)
```

Now let's store this collection of preferences as `day_to_day_coding`

```{r}
library("rstudioprefswitcher")
store_prefs(preferences_name = "day_to_day_coding")
```

We want to now prove that we can restore preferences, so let's make the taskbar visible again:

```{r}
rstudioapi::writeRStudioPreference("toolbar_visible", TRUE)
```

Now let's load up our stored set of preferences which will again hide the taskbar:

```{r}
new_preferences <- set_prefs(preferences_name = "day_to_day_coding")
```
